\chapter{Analysis}

\section{Introduction}
The clients i will be working with are Rob Curtis and Liz Jeffries who work for individual pubs. The company currntly uses selfwriten bespoke software in their pubs, however as good as their software is there are still a few loop holes. the current system manages all stock except for the kitnchen's and manages all retail. 
The problem with the current system is that its fails to promt the user about certain parts of the stock management system such as to label each item after it's details have been inputed into the system. The system also does not have a privileges system so stock can be added by anyone without being checked properly. The soultion to one theses problems is simple as it only involves adding a prompt to the user tellingthem to put labbels on the stock. the second is a bit more complex as is involes creating user accounts for each member of staff each with a diffrent of privileges.
The new system must be able to add stock to the data base as well as delet it, it must also be able to keep track of how much of one stock item is left for example how many pints left in a kilderkin as well as know when stock needs to be brought up from the cellar. the system should interact with social media such as twiter and tweet when a new barel is put on a pump as well as record how much stock has been wasted.
The most realist way to implment these soultions: For labelling stock, the system should prompt the user by asking them if they want to print of the stock labbels or simplely print out the labels and prompt the user on screen. For privileges the system could ask for a password when the user trys to enter stock onto the database or the user could log onto the system with a password and them when they tried to add stock the system would check the users privileges.
\subsection{Client Identification}
The clients I will be working with are the landlords of the haymakers pub, Rob Certis and Liz Jeffries, they are looking for a better system to help them better manage their stock. Rob and Liz both work for a company called individual pubs who own five pubs, one in each of Peterborough, Pondon, Porwich and two in Cambridge. individual pubs is a small company in a big industry and already use bespoke software that they have writen themselfs as they can not aford to pay the licensing of profetional software. Because of this it is important that they get to most out of what they can and cannot afford to keep losing stock like they have. Rob have asked and Liz for thier input on the project as they are the ones who use the fast range of functions the software has to provid on a daily bases
\subsection{Define the current system}

\subsection{Describe the problems}

\subsection{Section appendix}

\section{Investigation}

\subsection{The current system}

\subsubsection{Data sources and destinations}

\subsubsection{Algorithms}

\subsubsection{Data flow diagram}

\subsubsection{Input Forms, Output Forms, Report Formats}

\subsection{The proposed system}

\subsubsection{Data sources and destinations}

\subsubsection{Data flow diagram}

\subsubsection{Data dictionary}

\subsubsection{Volumetrics}

\section{Objectives}

\subsection{General Objectives}

\subsection{Specific Objectives}

\subsection{Core Objectives}

\subsection{Other Objectives}

\section{ER Diagrams and Descriptions}

\subsection{ER Diagram}

\subsection{Entity Descriptions}

\section{Object Analysis}

\subsection{Object Listing}

\subsection{Relationship diagrams}

\subsection{Class definitions}

\section{Other Abstractions and Graphs}

\section{Constraints}

\subsection{Hardware}

\subsection{Software}

\subsection{Time}

\subsection{User Knowledge}

\subsection{Access restrictions}

\section{Limitations}

\subsection{Areas which will not be included in computerisation}

\subsection{Areas considered for future computerisation}

\section{Solutions}

\subsection{Alternative solutions}

\subsection{Justification of chosen solution}
